---
title: "The R-Ladies Data Cleaning Gauntlet"
author: "Alice Walsh, R-Ladies Philly"
date: "8/2/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

Below I have assembled some data cleaning challenges! The data to clean is all available online.

This first code chunk loads the data. In RStudio, you can click a green arrow in the top right corner to run the chunk. You should see that a new variable appears in your Global Environment. 

```{r get_data}
data_link <- 'http://data.phl.opendata.arcgis.com/datasets/0707c1f31e2446e881d680b0a5ee54bc_0.csv'
df <- read.csv(data_link)
```

```{r load_packages}
# Do you want to load some packages here? Maybe tidyverse? 
# Here are the packages I loaded to do this! You made need more or different ones

library(tidyverse)
library(stringr)
```

# Challenge one

The first step is to inspect the data. Use 2 or three commands to look at things like...   

* What are the variable/column names?
* What data class are the variable/columns?
* How many NA's are there per variable?

```{r inspect}
# Put your code here!

```

# Challenge two

There is some missing data. Also some data has been converted to factors when it should be character.

Let's re-import the data with read.csv() and some options.

```{r reload_data}
# Fill in the options - add stringsAsFactors, na.strings
?read.csv
# Alternatively, use your favorite package to read in the data instead of read.csv()
df <- read.csv(data_link) # add here
```

# Challenge three

Let's clean up the NEIGHBORHOOD! Use all your favorite commands to look at the values in NEIGHBORHOOD and clean them up. There are some entries with an extra space. There is some inconsistent capitalization.


```{r clean_neighborhood}
# Your code here
```

# Challenge four

There are 48 values in the MONTHS variable. If you want to plot the number of farmer's markets by month, how will you do it?

Tip: Clean up the MONTHS variable and then add some new variables 

```{r clean_months}
# Add code to process data here

```

```{r plot_by_month}
# Code to plot markets by month - 
# Uncomment and Modify the below ggplot2 code or start fresh with your own code

# ggplot(by_month, aes(x = month, y = number)) +
#   geom_col()
```

# Extra challenges

Let's combine this data with another dataset? maybe something from opendataphilly?
What if you were asked to plot the markets by zip code? or by day of week?
What if you wanted to plot the markets on a map using the coordinates provided in X, Y?

# Bonus data reshape challenge

The farmers market data is not a great example to show converting between wide and long data. If you want to practice this, here is an interesting dataset.

* Zillow makes home prices and other data available on their website: https://www.zillow.com/research/data/


```{r load_widedata}
zillow_source <- "http://files.zillowstatic.com/research/public/Zip/Zip_MedianListingPrice_AllHomes.csv"
zillow_wide <- read.csv(zillow_source)
dim(zillow_wide)
```

The data is 10165 rows and 108 columns. Let's filter to just keep Philadelphia data:

```{r filter_zillow}
# This code uses filter from dplyr package - there are other ways you could do this
zillow_wide <- filter(zillow_wide, City == "Philadelphia")
```

This data is wide - there are columns for every month with home prices. Instead, we want to have one column with the prices and another with the month and year. How can we convert from wide to long?

```{r reshape_zillow}
# Create a new dataframe, zillow_long, that contains reshaped data

```

```{r plot_zillow}
# Now we can plot the prices over time for each Philadelphia RegionName (zip code)
# Here is some example code you can modify to fit your dataset or change to make prettier

# ggplot(zillow_long, aes(x = month, y = price, group = RegionName)) + 
#   geom_line() + 
#   facet_wrap(~year)
```

